\documentclass{article}
\usepackage[a4paper, margin=0.4in]{geometry}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{lipsum}
\begin{document}
\begin{flushleft}
\hspace{2mm}\textbf{Tushar Gurjar}\\
\hspace{2mm}Department of Computer Science and Engineering\\
\hspace{2mm}Indian Institute of Technology Kanpur, India\\
\hspace{2mm}\textit{Email: \href{mailto:tushargr@iitk.ac.in}{tushargr@iitk.ac.in}}
\end{flushleft}
\hrule width \hsize \kern 1mm \hrule width \hsize height 0.4pt 
The personal goals that I want to achieve as a student of the IIT KANPUR are in the education and career areas of my life. In my education, my major goal is to gain knowledge in computers and network administration, eventually culminating in a Bachelor of Technology in Computer Science. I also wish to strengthen my grammar and interpersonal skills. In my career, my goal is to either advance from my current career as a paralegal to that of an office manager or to enter into a different career as information technology department administrator. I will use staff and university services in order to achieve my goals in a reasonable time-frame with limited obstacles.
\hrule width \hsize \kern 1mm \hrule width \hsize height 0.4pt
\vspace{4mm}
\noindent\textbf{Education }\newline\newline
\begin{tabular}{|l|l|l|l|}
\hline
Matriculation & Year & Institute/School & Percentage/CGPA\\
\hline
 B.Tech & - & IIT Kanpur & 8.9\\
 \hline
 12th & 2015 & SPJV & 93.60 \%\\
 \hline
 B.Tech & 2013 & SPJV & 10\\
 \hline
\end{tabular}\newline\newline\newline
\textbf{Course Details}\newline\newline
\begin{tabular}{|l|l|l|}
 \hline
Semester & Total Credits & Highlights\\
\hline
Aug 2016 - Dec 2016  &  50  & ESC-101 , MTH-101 , ART-101A\\
 \hline
 Jan 2017 - Apr 2017  &  48  & MTH-102 , PHY-102\\
 \hline
Aug 2016 - Dec 2016  &  58  & CS-201 , CS-202, CS-203\\
 \hline
\end{tabular}
\newline\newline\newline
\textbf{Skills}\newline\newline
Computer Sciecnce : Algorithms, Operating systems, Machine learning\newline
Programming languages : C, C++, Python, Java, Scripting languages (bash, awk)
\newline\newline
\textbf{Projects}
\begin{enumerate}
   \item \textbf{Battleship Game AI using Reinforcement Learning}\newline                             \footnotesize{IIT Kanpur Programming Club}\hspace{110mm}\footnotesize{May 2017-July 2017}
   	\begin{itemize}
	\item \normalsize{The aim of the project was to make AI for battleship board game.}
	\item \normalsize{Implemented two models- Monte Carlo and Temporal difference learning to build the agent.}
	\end{itemize}
   \item \textbf{\normalsize{Image Analysis using Machine Learning}}\newline
   \footnotesize{IIT Kanpur Programming Club}\hspace{110mm}\footnotesize{May 2017-July 2017}
   	\begin{itemize}
	\item \normalsize{The aim of the project was to make a image analyser that can extract features like text from image.}
	\item \normalsize{Implemented text detection using MSER technique, word formation using geometric constraints, character  segmentation using connected components.}
    \item \normalsize{Finally used Convolutional Neural Network for character recognition.}
	\end{itemize}
\end{enumerate}
\textbf{Awards and achievements}
\renewcommand{\labelitemi}{\textendash}
\begin{itemize}
   \item  All India Rank 759 in JEE Advanced 2016.
   \item  Gold medal in essay competetion.
   \item  Gold medal in debate competition.
\end{itemize}
\textbf{Hobbies and Interests}
\renewcommand{\labelitemi}{\textendash}
\begin{itemize}
   \item  Competitive Programming, Machine learning.	
   \item  Sports: Cricket, Volleyball
   \item  Music: Piano, Flute, Classical
\end{itemize}
\end{document}
